\propertitle

### 2019-12-15 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-15T19:49:18+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\enquote{Cooperativity}, \enquote{interaction}, and similar terms are
vague, so we need to translate them into a more precise notion first. Here
we use the notion of \emph{informational sufficiency}
\citep{kullbacketal1951}[\sect~4.5]{bernardoetal1994}[\chap~8 and
\sect~14.2]{jaynes1994_r2003} because it relates to those terms and
especially because it is tightly connected with maximum-entropy
distributions. We now shortly explain its meaning and use; please see the
end of this section for a bibliography with in-depth discussions.

@@

This notion is useful in our present problem owing to its tight connection
with maximum-entropy distributions: \emph{if a probability distribution for
  repetitive phenomena has a sufficient statistics, then it is a mixture of
  distributions of maximum-entropy form}.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-15T20:01:34+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\enquote{Cooperativity}, \enquote{interaction}, and similar terms are
vague, so we need to translate them into a more precise notion first. Here
we use the notion of \emph{informational sufficiency}
\citep{kullbacketal1951}[\sect~4.5]{bernardoetal1994}[\chap~8 and
\sect~14.2]{jaynes1994_r2003} because it relates to those terms and
especially because it is tightly connected with maximum-entropy
distributions. We now shortly explain its meaning and use; please see the
end of this section for references to in-depth discussions and technical
results.

@@

This notion is useful in our present problem owing to its tight
mathematical connection with maximum-entropy distributions, in the form of
a theorem: \emph{if a probability distribution for repetitive phenomena has
  a sufficient statistics, then it is a mixture of distributions of
  maximum-entropy form, and vice versa}. Thus, maximum-entropy
distributions automatically appear (as approximations) from the
probability-calculus when we test hypotheses about sufficiency.
